Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-25 docs/manuscript/manuscript.tex
change of bib file name
Hyperlink of all the citations

\section{Introduction}
In 2017, 29\% of the global population (2.2 billion people) did not use a safely managed drinking-water service, which is defined as water located on-premises, available, and free from contamination \citep{WHOdrinkingwater}.   If you meet about 100 people, you can imagine that 29 of the people you meet do not have access to improved drinking water. Where this raises concerns about inequality problems related to the task and time variation 
to collect water can be inferred in the urban and rural areas \citep{cassivi2018access}. Therefore, there needs to be a
great motivation to bring improved drinking water sources to all people to improve their quality of life.

@@

Globally, access to improved drinking water sources and sanitation is increasing. From 1990 to 2012, the utilization of
improved drinking water sources has increased globally from 76 percent to 89 percent, and utilization of improved
sanitation has increased from 45 percent to 64 percent \citep{fuller2016tracking}. According to the Millennium Development Goals (MDGs),
they consider improved drinking water sources like the following: public tap, borehole, protected spring, rainwater
collection, bottled water source, and piped water \citep{bartram_global_2014}. However, these variables do not truly
explain if the households have speedy access to retrieve the water. Additionally, \citet{graham_analysis_2016} investigated that many people in sub-Saharan Africa (SSA) leave their homes to retrieve water, potentially placing them at risk for a variety of negative health outcomes. There are an estimation of 3.36 million children and 13.54 million adult females were responsible for collection in households with fetching times greater than 30 minutes \citep{graham_analysis_2016}. Therefore, there needs to be a way to alleviate people's burdens to retrieve water and potentially investigate water accessibility improving variables.

@@

\citet{jagals2006does} highlights in a case study in a rural area in South Africa discovered providing small communities. The rural area used untreated river water as their water source. The Researchers installed good quality water with a piped distribution system and increase accessibility by installing communal taps. However, this implementation did not fall within the parameters of safe water. This didn't increase household quantities, which remained around 18 L per person per day. Their research
gives a potential understanding even making the drinking water accessible might not improve the quality of the water
itself.

\citet{onda2012global} discusses the global access to safe water by accounting for water quality and the resulting
impact on (MDGs) progress. They altered the current Joint Monitoring Programme (JMP) estimation by accounting for microbial
water quality and sanitary risk utilizing national water quality data. 
Overall, their analysis highlights the potential fatigue can have causes that aren't due to underlying disease. The main example would be heavy exertion of carrying water.  Improvement of modes of transportation can enhance water accessibility which can improve one's health overall. 
modes of transportation can affect one's health.

\citet{sima2013water} highlights the relation of the topic where it discovered that over 76 percent of the city's water
is utilized by less than ten percent of household piped water.  The study is focused on Kisumu Kenya and Sima
interviewed 260 informal water business operators. This article revealed a new insight where the majority of the
population in Kisumu relied on purchased water from kiosks (1.5 million $m^{3}$ per day) and used hand-drawn water-carts
(0.75 million $m^{3}$ per day)\citep{sima2013water}. Also, we discovered that the water trucking industry utilized the
most energy consumption and was high cost: water delivery trucks have the highest per cubic meter energy demand (35
$MJ/m^{3}$)\citep{sima2013water}.

\citet{ho2014challenge} investigates a head-to-head comparison of such indicators with other possible distance and time
metrics among rural 1,103 households in Nampula province, Mozambique. The researchers found out that Euclidean line
distance to be a good representative for route distance ($R^{2} = 0.98$), while self-reported travel time is a poor
representative ($R^{2} = 0.12$). One of the key insights was that a 15-minute decrease in one-way walk time to a water source
is related to a 41\% reduction in diarrhea, improved children's nutrition, and an 11\% reduction in under-five child
mortality rate \citep{ho2014challenge}.

\citet{bartram2014globala} highlights background information about the Millennium Development Goals. How it has
established global targets for drinking water and sanitation access (Bartram et al. 2014). The article indirectly gives
much information about progress towards focused targets, directed by international monitoring, has reduced the global
disease burden and improved the quality of life \citep{bartram2014globala}. It utilizes a variety of sources such as
JMP, DHS, MICS surveys to analyze the data of many different locations in the world, therefore, it is a broad scope of
study of the progress of accessible and drinking water and sanitation globally. Our research can study further what
modes of transportation of clean drinking water would affect the progress of improving drinking water and sanitation in
one's community.

\citet{onda2014country} proposed a country typology based on nine water and sanitation indicators. They applied hierarchical clustering to 156 countries, accounting for 6.75 billion people (93\%). This work improves on previous geography or income-based country clustering.

\citet{WHOdrinkingwater} article gives an ambitious plan to reach universal drinking water by the year 2030 that is
affordable and safe followed by the Sustainable Development Goal six goals. The WHO/UNICEF Joint Monitoring Program for
Water Supply and Sanitation (JMP) have been globally monitoring progress on drinking water and sanitation since 1990. \citet{WHOdrinkingwater} outlines different plans with consistent traits to determine what is deemed to be safe and affordable drinking
water and good sanitation.

\citet{fuller2016tracking} analyzes the global accessibility to safe drinking water and sanitation and concludes that
it has been improving well during the Millennium Development Goal Period. \citet{fuller2016tracking} chose some countries and studied the overall countries
progress which in his methodology revealed sigmoidal trends. Our study can reveal if certain methods of transportation
of drinking water and sanitation may have influenced the effectiveness of the improved drinking water met by MDGs
standards.

\citet{jia2016highresolution} highlights that there is inequality within safe sanitation. There is a great difference in
wealth levels in many low-income countries. Therefore, this will hinder the improvement of MDG
progress. \citet{jia2016highresolution}discusses future interventions to be engaged with different wealth
categories. Our study can assist in understanding improved sanitation increase by making inferences about how they
receive water may give the community focusing on sanitation. Overall, income inequality affects who will have access to
proper sanitation.

\citet{cassivi2018access} highlights about how there should be more information to the effect of including a 30-minute
collection time to monitor access to drinking water. The lack of access to on-premises water sources can cause the use
of greater distant alternative sources. Therefore causing the quantity of retrieved water to reduce as the water plateau
phenomenon.\citet{cassivi2018access} hypothesizes that the households who must travel further are using unimproved
sources. For our research, we can discover what modes of transportation people are traveling to retrieve the water and
in what quantity depending on their means of transportation. Therefore, learning how to decrease the travel time of
people to retrieve the water because according to the article, it can be a great burden and does not increase the
quality of one's life to retrieve water daily and far away from their homes.

\citet{tortajada2018achieving} highlights that sharing the immense improvement at the 2015 convention negatively
affected many people because they actually have not acquired clean drinking water. While 2.6 billion people gained
access to drinking water, they did not have constructive feedback on the quality of the water. Also, our research can
fill in the blank on how did these people actually retrieve the water? Our research can measure the performance of how
people retrieve water which may not be in their premises.

\citet{amit2019measuring} highlights their data analysis similar to what we will be doing and found out that for
non-piped households, collection costs are 22\% of the coping costs, while collection costs for piped households are
less than 2\% of the coping costs. The researchers also realize that there is economic inequality because the majority
of the piped households are in households that are considered wealthy households and vice versa. Our research can
pinpoint how households are traveling to collect water to improve potential policy-making for water accessibility.

\citet{price2019difference} highlights the temporal dynamics of drinking water access and quality in urban slums which
is home to about 1 billion people globally. \citet{price2019difference} discusses the temporal changes in drinking water
access and quality in urban slums may influence on health risks. \citet{price2019difference} believes that monitoring
temporal dynamics should be considered over three interlinked time scales: short, medium and long term.

\citet{price2019difference} recommends future research to explore the short-term water access and quality monitoring. Also we should learn to recognize the role of socio-cultural factors that may impact the temporal dynamics of safe water access. Our project can pinpoint additional water accessibility variables that can be used to focus to recognize the time variations as well.

\citet{rawas2020comparing} highlights the need for different approaches of intermittent water supplies (IWS) to monitor piped water supply perpetually in Peru. This relates and informs one mode of transportation of clean and accessible water. Our research can make inferences about if the customers receive clean water elsewhere, such as water tankers, kiosks, vendors, etc. Overall, the article found that the percent of households with (IWS) was a few percentage points greater than of the reported utilities.

\citet{deshpande2020mapping} discusses their findings of improved overall water availability and piped water accessibility for the globe (40\% to 50.3\%). \citet{deshpande2020mapping} also found that it was the lowest increase in sub-Saharan Africa, where the accessibility was mostly concentrated in urban regions. \citet{deshpande2020mapping} focuses mostly on understanding trends in diarrhea burden, where the needs are greatest for the improvement of access to safe drinking water and sanitation facilities. Our study can benefit this research by implementing the best and effective modes of transportation of clean water to improve safe drinking water and sanitation. Even with the water pipe access increasing, they can't conclude if the people had clean water as they needed right away. Overall, the access to safe drinking water and sanitation improved globally between 2000 and 2017, but dis-proportionality undermines reaching the Sustainable Development Goals.

\citet{goal} explains specific targets that have goals and indicators to track global water accessibility. The article quantifies and provides Graphs: safe drinking water, safe sanitation, and hygiene, safe sanitation and hygiene, ambient water quality, water use efficiency, levels of freshwater stress, integrated water management, trans-boundary water cooperation, protect and restore water-related ecosystems, water and sanitation support, local participation in sanitation management. They have many ambitious plans to achieve by 2020 and 2030, and our research can find a correlation to why achieving this may be possible.

\citet{cassivi2021evaluating} focuses a case study in Southern Malawi, where data collected in March and April of 2019 at the conclusion of the rainy season. The sample was consisted of 375 households without access to water on their premises.   The article highlighted using Euclidean Distance measurement is more reliable than the self-reported time. Also queuing time measurement can be hard to be measured because of their ambiguity. Their research gives greater insight into how do we define water accessibility and how increase of water accessibility can impact people's lives beneficially.

@@

Next, there were many missing values from the data. Therefore, we had to do a simple missing value analysis. We determined to avoid using water, transportation, or wealth variables which had greater than 50\% missing values. Ultimately, simplified data frame was 76 countries by 28 variables. After, two different tables are generated where one focused on the water accessibility variables and a explanatory variables. We selected 11 water accessibility variables based on the sources available such as location, time, and methodology \citep{price2019difference}. The water accessibility variable was organized
in the following table to allow for quick visualization for \autoref{tab:summary-wa}. The other variables were used as an explanatory variables for determining the water accessibility predictors in \autoref{tab:summary-var}. 
\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{ptap} &  Public tap/standpipe
 & 
 \\\midrule
 \texttt{bore} & Tube well/borehole & 
\\\midrule
\texttt{pspr} & Protected spring
& 
\\\midrule
\texttt{uspr} & Unprotected spring
& 
\\\midrule
\texttt{pwel} & Protected well
& 
\\\midrule
\texttt{uwel} & Unprotected well water
&
\\\midrule
\texttt{surw} & Surface water
& 
\\\midrule
\texttt{tles} & Water 30 minutes or less away round trip
&
\\\midrule 
\texttt{tmor} & Water more than 30 minutes away round trip & 
\\\midrule
\texttt{rain} & Rainwater
& 
\\\midrule
\texttt{phom} & Piped into dwelling
&
\\\midrule

& \\\bottomrule
  \end{tabular}
  \caption{Summary of water accessibility variables (National Household usage Averages measured as percentage for Main Drinking Source)}
  \label{tab:summary-wa}
\end{table}

\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{imws} & Improved water source
 & 
 \\\midrule
  \texttt{pipy} & Water piped into yard/plot
&
\\\midrule
 \texttt{truc} & Tanker truck & 
\\\midrule
 \texttt{ctan} & Cart with tank & 
\\\midrule
 \texttt{bott} & Bottled water & Drinking water is bottled water/demi john.
\\\midrule
 \texttt{uiws} & Unimproved water source & 
\\\midrule
 \texttt{othw} & Other water source & 
\\\midrule
 \texttt{iwsp} & Improved water source on the premises & The de jure population living in households with an improved water source on the premises.
\\\midrule
 \texttt{basw} & Basic water service
 & Defined as an improved water source with either water on the premises or round-trip collection time is 30 minutes or less.
\\\midrule
 \texttt{liws} & Limited water service
 & Limited water service, defined as an improved water source with round-trip collection time greater than 30 minutes.
\\\midrule
 \texttt{prem} & Water on the premises
 & 
\\\midrule
 \texttt{bicy} & Bicycle
 &
\\\midrule
 \texttt{acar} & Animal drawn cart
 & 
\\\midrule
 \texttt{mcyc} & Motorcycle
 & 
\\\midrule
 \texttt{pcar} & Private car
 & 
\\\midrule
 \texttt{boat} & Boat with a motor
 & 
\\\midrule
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country.
\\\midrule
 & \\\bottomrule
  \end{tabular}
  \caption{Summary of explanatory variables (National Household usage Averages measured as percentage for Main Drinking Source)}
  \label{tab:summary-var}
\end{table}
 \subsection*{Summary of variables}
\hl{Here, you show and discuss the data distributions (e.g. histograms, correlation plots, etc)}

>>>>

\section{Introduction}
In 2017, 29\% of the global population (2.2 billion people) did not use a safely managed drinking-water service, which is defined as water located on-premises, available, and free from contamination \citep{whoDrinkingwater}.   If you meet about 100 people, you can imagine that 29 of the people you meet do not have access to improved drinking water. Where this raises concerns about inequality problems related to the task and time variation 
to collect water can be inferred in the urban and rural areas \citep{cassiviAccessDrinkingWater2018}. Therefore, there needs to be a
great motivation to bring improved drinking water sources to all people to improve their quality of life.

@@

Globally, access to improved drinking water sources and sanitation is increasing. From 1990 to 2012, the utilization of
improved drinking water sources has increased globally from 76 percent to 89 percent, and utilization of improved
sanitation has increased from 45 percent to 64 percent \citep{fullerTrackingProgressGlobal2016}. According to the Millennium Development Goals (MDGs),
they consider improved drinking water sources like the following: public tap, borehole, protected spring, rainwater
collection, bottled water source, and piped water \citep{bartramGlobalMonitoringWater2014}. However, these variables do not truly
explain if the households have speedy access to retrieve the water. Additionally, \citet{grahamAnalysisWaterCollection2016} investigated that many people in sub-Saharan Africa (SSA) leave their homes to retrieve water, potentially placing them at risk for a variety of negative health outcomes. There are an estimation of 3.36 million children and 13.54 million adult females were responsible for collection in households with fetching times greater than 30 minutes \citep{grahamAnalysisWaterCollection2016}. Therefore, there needs to be a way to alleviate people's burdens to retrieve water and potentially investigate water accessibility improving variables.

@@

\citet{jagalsDoesImprovedAccess2006} highlights in a case study in a rural area in South Africa discovered providing small communities. The rural area used untreated river water as their water source. The Researchers installed good quality water with a piped distribution system and increase accessibility by installing communal taps. However, this implementation did not fall within the parameters of safe water. This didn't increase household quantities, which remained around 18 L per person per day. Their research
gives a potential understanding even making the drinking water accessible might not improve the quality of the water
itself.

\citet{ondaGlobalAccessSafe2012} discusses the global access to safe water by accounting for water quality and the resulting
impact on (MDGs) progress. They altered the current Joint Monitoring Programme (JMP) estimation by accounting for microbial
water quality and sanitary risk utilizing national water quality data. 
Overall, their analysis highlights the potential fatigue can have causes that aren't due to underlying disease. The main example would be heavy exertion of carrying water.  Improvement of modes of transportation can enhance water accessibility which can improve one's health overall. 
modes of transportation can affect one's health.

\citet{simaWaterFlowsEnergy2013} highlights the relation of the topic where it discovered that over 76 percent of the city's water
is utilized by less than ten percent of household piped water.  The study is focused on Kisumu Kenya and Sima
interviewed 260 informal water business operators. This article revealed a new insight where the majority of the
population in Kisumu relied on purchased water from kiosks (1.5 million $m^{3}$ per day) and used hand-drawn water-carts
(0.75 million $m^{3}$ per day)\citep{simaWaterFlowsEnergy2013}. Also, we discovered that the water trucking industry utilized the
most energy consumption and was high cost: water delivery trucks have the highest per cubic meter energy demand (35
$MJ/m^{3}$)\citep{simaWaterFlowsEnergy2013}.

\citet{hoChallengeGlobalWater2014} investigates a head-to-head comparison of such indicators with other possible distance and time
metrics among rural 1,103 households in Nampula province, Mozambique. The researchers found out that Euclidean line
distance to be a good representative for route distance ($R^{2} = 0.98$), while self-reported travel time is a poor
representative ($R^{2} = 0.12$). One of the key insights was that a 15-minute decrease in one-way walk time to a water source
is related to a 41\% reduction in diarrhea, improved children's nutrition, and an 11\% reduction in under-five child
mortality rate \citep{hoChallengeGlobalWater2014}.

\citet{bartramGlobalMonitoringWater2014} highlights background information about the Millennium Development Goals. How it has
established global targets for drinking water and sanitation access (Bartram et al. 2014). The article indirectly gives
much information about progress towards focused targets, directed by international monitoring, has reduced the global
disease burden and improved the quality of life \citep{bartramGlobalMonitoringWater2014}. It utilizes a variety of sources such as
JMP, DHS, MICS surveys to analyze the data of many different locations in the world, therefore, it is a broad scope of
study of the progress of accessible and drinking water and sanitation globally. Our research can study further what
modes of transportation of clean drinking water would affect the progress of improving drinking water and sanitation in
one's community.

\citet{ondaCountryClusteringApplied2014} proposed a country typology based on nine water and sanitation indicators. They applied hierarchical clustering to 156 countries, accounting for 6.75 billion people (93\%). This work improves on previous geography or income-based country clustering.

\citet{whoDrinkingwater} article gives an ambitious plan to reach universal drinking water by the year 2030 that is
affordable and safe followed by the Sustainable Development Goal six goals. The WHO/UNICEF Joint Monitoring Program for
Water Supply and Sanitation (JMP) have been globally monitoring progress on drinking water and sanitation since 1990. \citet{whoDrinkingwater} outlines different plans with consistent traits to determine what is deemed to be safe and affordable drinking
water and good sanitation.

\citet{fullerTrackingProgressGlobal2016} analyzes the global accessibility to safe drinking water and sanitation and concludes that
it has been improving well during the Millennium Development Goal Period. \citet{fullerTrackingProgressGlobal2016} chose some countries and studied the overall countries
progress which in his methodology revealed sigmoidal trends. Our study can reveal if certain methods of transportation
of drinking water and sanitation may have influenced the effectiveness of the improved drinking water met by MDGs
standards.

\citet{jiaHighResolutionSpatialDistribution2016} highlights that there is inequality within safe sanitation. There is a great difference in
wealth levels in many low-income countries. Therefore, this will hinder the improvement of MDG
progress. \citet{jiaHighResolutionSpatialDistribution2016}discusses future interventions to be engaged with different wealth
categories. Our study can assist in understanding improved sanitation increase by making inferences about how they
receive water may give the community focusing on sanitation. Overall, income inequality affects who will have access to
proper sanitation.

\citet{cassiviAccessDrinkingWater2018} highlights about how there should be more information to the effect of including a 30-minute
collection time to monitor access to drinking water. The lack of access to on-premises water sources can cause the use
of greater distant alternative sources. Therefore causing the quantity of retrieved water to reduce as the water plateau
phenomenon.\citet{cassiviAccessDrinkingWater2018} hypothesizes that the households who must travel further are using unimproved
sources. For our research, we can discover what modes of transportation people are traveling to retrieve the water and
in what quantity depending on their means of transportation. Therefore, learning how to decrease the travel time of
people to retrieve the water because according to the article, it can be a great burden and does not increase the
quality of one's life to retrieve water daily and far away from their homes.

\citet{tortajadaAchievingUniversalAccess2018} highlights that sharing the immense improvement at the 2015 convention negatively
affected many people because they actually have not acquired clean drinking water. While 2.6 billion people gained
access to drinking water, they did not have constructive feedback on the quality of the water. Also, our research can
fill in the blank on how did these people actually retrieve the water? Our research can measure the performance of how
people retrieve water which may not be in their premises.

\citet{amitMeasuringAffordabilityAccess2019} highlights their data analysis similar to what we will be doing and found out that for
non-piped households, collection costs are 22\% of the coping costs, while collection costs for piped households are
less than 2\% of the coping costs. The researchers also realize that there is economic inequality because the majority
of the piped households are in households that are considered wealthy households and vice versa. Our research can
pinpoint how households are traveling to collect water to improve potential policy-making for water accessibility.

\citet{priceDifferenceDayCan2019} highlights the temporal dynamics of drinking water access and quality in urban slums which
is home to about 1 billion people globally. \citet{priceDifferenceDayCan2019} discusses the temporal changes in drinking water
access and quality in urban slums may influence on health risks. \citet{priceDifferenceDayCan2019} believes that monitoring
temporal dynamics should be considered over three interlinked time scales: short, medium and long term.\citet{priceDifferenceDayCan2019} recommends future research to explore the short-term water access and quality monitoring. Also we should learn to recognize the role of socio-cultural factors that may impact the temporal dynamics of safe water access. Our project can pinpoint additional water accessibility variables that can be used to focus to recognize the time variations as well.

\citet{rawasComparingUtilityreportedHours2020} highlights the need for different approaches of intermittent water supplies (IWS) to monitor piped water supply perpetually in Peru. This relates and informs one mode of transportation of clean and accessible water. Our research can make inferences about if the customers receive clean water elsewhere, such as water tankers, kiosks, vendors, etc. Overall, the article found that the percent of households with (IWS) was a few percentage points greater than of the reported utilities.

\citet{deshpandeMappingGeographicalInequalities2020} discusses their findings of improved overall water availability and piped water accessibility for the globe (40\% to 50.3\%). \citet{deshpandeMappingGeographicalInequalities2020} also found that it was the lowest increase in sub-Saharan Africa, where the accessibility was mostly concentrated in urban regions. \citet{deshpandeMappingGeographicalInequalities2020} focuses mostly on understanding trends in diarrhea burden, where the needs are greatest for the improvement of access to safe drinking water and sanitation facilities. Our study can benefit this research by implementing the best and effective modes of transportation of clean water to improve safe drinking water and sanitation. Even with the water pipe access increasing, they can't conclude if the people had clean water as they needed right away. Overall, the access to safe drinking water and sanitation improved globally between 2000 and 2017, but dis-proportionality undermines reaching the Sustainable Development Goals.

\citet{GoalCleanWater} explains specific targets that have goals and indicators to track global water accessibility. The article quantifies and provides Graphs: safe drinking water, safe sanitation, and hygiene, safe sanitation and hygiene, ambient water quality, water use efficiency, levels of freshwater stress, integrated water management, trans-boundary water cooperation, protect and restore water-related ecosystems, water and sanitation support, local participation in sanitation management. They have many ambitious plans to achieve by 2020 and 2030, and our research can find a correlation to why achieving this may be possible.

\citet{cassiviEvaluatingSelfreportedMeasures2021} focuses a case study in Southern Malawi, where data collected in March and April of 2019 at the conclusion of the rainy season. The sample was consisted of 375 households without access to water on their premises.   The article highlighted using Euclidean Distance measurement is more reliable than the self-reported time. Also queuing time measurement can be hard to be measured because of their ambiguity. Their research gives greater insight into how do we define water accessibility and how increase of water accessibility can impact people's lives beneficially.

@@

Next, there were many missing values from the data. Therefore, we had to do a simple missing value analysis. We determined to avoid using water, transportation, or wealth variables which had greater than 50\% missing values. Ultimately, simplified data frame was 76 countries by 28 variables. After, two different tables are generated where one focused on the water accessibility variables and a explanatory variables. We selected 11 water accessibility variables based on the sources available such as location, time, and methodology \citep{price2019difference}. The water accessibility variable was organized
in the following table to allow for quick visualization for \autoref{tab:summary-wa}. The other variables were used as an explanatory variables for determining the water accessibility predictors in \autoref{tab:summary-var}. 
\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{ptap} &  Public tap/standpipe
 & 
 \\\midrule
 \texttt{bore} & Tube well/borehole & 
\\\midrule
\texttt{pspr} & Protected spring
& 
\\\midrule
\texttt{uspr} & Unprotected spring
& 
\\\midrule
\texttt{pwel} & Protected well
& 
\\\midrule
\texttt{uwel} & Unprotected well water
&
\\\midrule
\texttt{surw} & Surface water
& 
\\\midrule
\texttt{tles} & Water 30 minutes or less away round trip
&
\\\midrule 
\texttt{tmor} & Water more than 30 minutes away round trip & 
\\\midrule
\texttt{rain} & Rainwater
& 
\\\midrule
\texttt{phom} & Piped into dwelling

 \\\bottomrule
  \end{tabular}
  \caption{Summary of water accessibility variables (National Household usage Averages measured as percentage for Main Drinking Source)}
  \label{tab:summary-wa}
\end{table}

\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{imws} & Improved water source
 & 
 \\\midrule
  \texttt{pipy} & Water piped into yard/plot
&
\\\midrule
 \texttt{truc} & Tanker truck & 
\\\midrule
 \texttt{ctan} & Cart with tank & 
\\\midrule
 \texttt{bott} & Bottled water & Drinking water is bottled water/demi john.
\\\midrule
 \texttt{uiws} & Unimproved water source & 
\\\midrule
 \texttt{othw} & Other water source & 
\\\midrule
 \texttt{iwsp} & Improved water source on the premises & The de jure population living in households with an improved water source on the premises.
\\\midrule
 \texttt{basw} & Basic water service
 & Defined as an improved water source with either water on the premises or round-trip collection time is 30 minutes or less.
\\\midrule
 \texttt{liws} & Limited water service
 & Limited water service, defined as an improved water source with round-trip collection time greater than 30 minutes.
\\\midrule
 \texttt{prem} & Water on the premises
 & 
\\\midrule
 \texttt{bicy} & Bicycle
 &
\\\midrule
 \texttt{acar} & Animal drawn cart
 & 
\\\midrule
 \texttt{mcyc} & Motorcycle
 & 
\\\midrule
 \texttt{pcar} & Private car
 & 
\\\midrule
 \texttt{boat} & Boat with a motor
 & 
\\\midrule
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country.
  \\\bottomrule
  \end{tabular}
  \caption{Summary of explanatory variables (National Household usage Averages measured as percentage for Main Drinking Source)}
  \label{tab:summary-var}
\end{table}
 \subsection*{Summary of variables}
\hl{Here, you show and discuss the data distributions (e.g. histograms, correlation plots, etc)}
